%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Mark}{Mavis}{ 
    % \runsubsection{Computer Science \& Software Engineering Graduate seeking Internships}\\
    \urlstyle{same}
    
    \href{https://www.linkedin.com/in/markwmavis/}{linkedin.com/MarkWMavis }| \href{https://github.com/MarkWMavis}{Github.com/MarkWMavis}  \\
    Woodiville, WA | \href{tel:+14256818886}{425.681.8886} | \href{mailto:mmavis@uw.edu}{mmavis@uw.edu}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.35\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Bachelors of Science}
\subsection{in Computer Science \&}
\subsection{Software Engineering}
\descript{University of Washington}
\location{Expected Grad. Jun '22 | Bothell, WA}
%College of Engineering \\
\location{Major GPA: 3.70 / 4.0
}
\sectionsep

\subsection{Associate in Science}
\descript{Cascadia College}
\location{Jan '18 - Jun '19 | Bothell, WA}
\location{ Major GPA: 3.71 / 4.0 
}
\sectionsep

\section{Honors \& Awards}
\runsubsection{Deans List}
\descript{| UW }
\location{Spring '21, '20 | Autumn '21, '20}
\runsubsection{Honor Society}
\descript{| UW }
\location{Tau Sigma Member since March '20}
\runsubsection{Presidents Honors}
\descript{| Cascadia }
\location{Winter '19}
\runsubsection{Faculty Honors}
\descript{| Cascadia }
\location{Spring '17}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Links} 
% Facebook:// \href{https://facebook/dd}{\bf dd} \\
% Github:// \href{https://github.com/deedydas}{\bf deedydas} \\
% LinkedIn://  \href{https://www.linkedin.com/in/debarghyadas}{\bf debarghyadas} \\
% YouTube://  \href{https://www.youtube.com/user/DeedyDash007}{\bf DeedyDash007} \\
% Twitter://  \href{https://twitter.com/debarghya_das}{\bf @debarghya\_das} \\
% Quora://  \href{https://www.quora.com/Debarghya-Das}{\bf Debarghya-Das}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills \& Experience}
\subsection{Programming Languages}
\location{High Lvl. Languages}
C++ \textbullet{}   C \textbullet{} C\# \textbullet{} Python \textbullet{} Java \\
\location{Low Lvl. Languages}
Assembly: ARM \& Thumb2 \\
\subsection{Engineering Software: }
Visual Studio \textbullet{} VS Code \textbullet{} Git \textbullet{} Matlab \\
Google Collaboratory \textbullet{} Unity \textbullet{} Logism \\
Keil Microvision \textbullet{} Project Manager \\
Figma \textbullet{} Adobe Suite \textbullet{} Autodesk CAD\\
\subsection{Web Development}
CSS \textbullet{} HTML \textbullet{} JavaScript \\
\subsection{Project Management}
Scrum \textbullet{} Agile \textbullet{} Waterfall  \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
% \subsection{Graduate}
% Advanced Machine Learning \\
% Open Source Software Engineering \\
% Advanced Interactive Graphics \\
% Compilers + Practicum \\
% Cloud Computing \\
% Evolutionary Computation \\
% Defending Computer Networks \\
% Machine Learning \\
% \sectionsep

\subsection{Undergraduate}
Machine Intelligence \\
Data Mining \& Pattern Recognition \\
Data Structures and Algorithms I \& II \\
Hardware \& Microcontrollers\\
Operating Systems \\
Software Project Management \\
Software \& Usability Engineering \\
Calculus 1, 2, 3 \& Physics 1, 2 \\
Matrix Algebra \& Discrete Mathematics\\
Game Development\\
% {\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst 2x) }}} \\
% Unix Tools and Scripting \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.64\textwidth} 

% \runsubsection{Coursera}
% \descript{| KPCB Fellow + Software Engineering Intern }
% \location{June 2014 – Sep 2014 | Mountain View, CA}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
% \begin{tightemize}
% \item 52 out of 2500 applicants chosen to be a KPCB Fellow 2014.
% \item Led and shipped Yoda - the admin interface for the new Phoenix platform. 
% \item Full-stack developer - Wrote and reviewed code for JS using Backbone, Jade, Stylus and Require and Scala using Play
% \end{tightemize}
% \sectionsep

% \runsubsection{Google}
% \descript{| Software Engineering Intern }
% \location{May 2013 – Aug 2013 | Mountain View, CA}
% \begin{tightemize}
% \item Worked on the YouTube Captions team, in Javascript and Python to plan, to design and develop the full stack to add and edit Automatic Speech Recognition captions. In production.
% \item Created a backbone.js-like framework for the Captions editor.
% \end{tightemize}
% \sectionsep

% \runsubsection{Phabricator}
% \descript{| Open Source Contributor \& Team Leader}
% \location{Jan 2013 – May 2013 | Palo Alto, CA \& Ithaca, NY}
% \begin{tightemize}
% \item Phabricator is used daily by Facebook, Dropbox, Quora, Asana and more.
% \item I created the Meme generator and more in PHP and Shell.
% \item Led a team from MIT, Cornell, IC London and UHelsinki for the project.
% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{University Research}
\runsubsection{\href{https://colab.research.google.com/drive/11OrfO4j-lhP-BlNuPEAn9pYZbiehlyr-?usp=sharing}{Deep Learning and Machine Vision in Agriculture}}
\descript{| Undergraduate Researcher}
\location{Sep 2021 – Dec 2021 | Bothell, WA}
Under \textbf{\href{https://sites.google.com/uw.edu/dais-uw/home?authuser=0}{Dr. Dong Si}}, researched the effects of image color balance on Machine Vision and ML model accuracy. \newline
    \begin{tightemize}
        \item \textbf{Machine Learning: } Engineered model using Tensorflows’ Keras deep learning API to identify object classes at 97\% success rate.
        \item \textbf{Computer Vision: } Implemented Pythons Computer Vision library to generate delimited pixel files to modularize proceeding tasks.
        \item \textbf{Data Processing: } Simulated various lighting conditions through data set pixel manipulation using Adobe software. \item 
        \textbf{Training Bias Reduction: } Configured the randomization of delimited data using SciKit library reducing training bias \& improving accuracy by over 30\%.
        \item \textbf{Testing Configuration: } Developed flexible testing algorithm using Google Colab to accelerate iterations. 
        \item \textbf{Refined Model Accuracy: } Successfully proved initial hypothesis and identified an 11\% increase in model accuracy using Matplotlib library.
    \end{tightemize}
\sectionsep

\runsubsection{\href{https://drive.google.com/file/d/1hJzap162z4QhbNTTLVZgvl25AcmKWR-z/view}{M.L. Modeling in Medical Ultrasound Imaging}}
\descript{| Undergraduate Researcher}
\location{Sep 2021 – Jan 2022 | Bothell, WA}
Under \textbf{\href{https://www.uwb.edu/css/faculty/bios/eparsons}{Prof Erika Parsons, ph.D.}}, Analyzed CT scans of traumatic brain injury patients to predict internal head trauma on Ultrasound.
\begin{tightemize}
\item \textbf{Data Analysis: } Implemented statistical analysis on 3 dimensional tissue density data for both CT and ultrasound scans to identify patterns.
\item \textbf{Dimensionality Reduction: } Engineered a reduced approximation of the data using Principle Component Analysis and Singular Value Decomposition.
\item \textbf{Formulated Predictions} Created proprietary blood scan predictions script using principle components and Matlab.
\end{tightemize}
\sectionsep

\section{Coding Projects}
\runsubsection{\href{https://github.com/MarkWMavis}{GITHUB}}
\descript{| Repositories}
\begin{tabularx}{1\textwidth} { 
   >{\raggedright\arraybackslash}X 
   >{\raggedright\arraybackslash}X 
   >{\raggedright\arraybackslash}X }
% \hline

 \href{https://github.com/MarkWMavis/CSS_343_DataStructures_II/tree/main/04_InventorySystem}{Movie Inventory} & 
 \href{https://github.com/MarkWMavis/CSS_343_DataStructures_II/tree/main/03_DijkstraShortestPath}{Dijkstra Algo.} & 
 \href{https://github.com/MarkWMavis/CSS_342_DataStructures_I/tree/main/04_MergeSort}{Sorting Algos} \\
 %\hline
 \href{https://github.com/MarkWMavis/CSS_430_OperatingSystems/tree/main/P3_Scheduling\%20Algorithms}{CPU Scheduling}  & 
 \href{https://github.com/MarkWMavis/CSS_430_OperatingSystems/tree/main/P1_2_Unix\%20Shell}{Shell Implementation} & 
 \href{https://markwmavis.github.io/CSS_385_HelloWorld/}{Hello World Game} \\
%\hline
\end{tabularx}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Work Experience}
\runsubsection{Lead sales and Operations Manager}
\descript{| Mavis Vacation Rentals}
\location{Jan 2015 – current | Woodinville, WA}
Established 
\begin{tightemize}
    \item \textbf{Success Generation: } Delivered over half a million in gross income in 5 years.
    \item \textbf{Growth Management: } Delivered 80\% Growth in bookings, produced 59\% increase in occupancy rate, and boosted revenue by 75\%  since inception.
    \item \textbf{Client Relations: } Consulted on all client hospitality, achieving top 5 market rank with 85+ 5-star ratings, a 94\% 5-rating. 
    \item \textbf{Market Analysis: } Implemented custom local market pricing strategy, producing a 93\% occupancy rate, outperforming competition.
    \item \textbf{Operations Efficiency: } Implemented remote management strategy to decrease utility expenses by over 25\%, maximizing available resources.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% \begin{tabular}{rll}
% 2014	     & top 52/2500  & KPCB Engineering Fellow\\
% 2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
% 2013	     & National  & Jump Trading Challenge Finalist\\
% 2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
% 2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
% 2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
